---
title: "Sivakumar Final Project"
author: "Ritesh Sivakumar"
format: html
---

#Quarto

```{r}
#| include: false
library (medicaldata)
library (tidyverse)
library(gtsummary)
```

```{r}
#| include: false
#table cleaning
#data (package = "medicaldata")
lic <- medicaldata::licorice_gargle
lico <- lic[, -11:-12:-13:-14:-15:-16:-17:-18:-19]
lico_cols <- c("sex", "asa", "bmi", "age", "mallampati", "smoking", "pain", "treat", "surgerysize",
							 "extubationcough")
```

```{r}
#| label: tbl-descr
#| tbl-cap: "Descriptive statistics"
#| output-location: slide
#gtsumamry table
tbl_summary(
		lico,
		by = preOp_gender,
		include = c(preOp_gender, preOp_asa,
								 preOp_calcBMI, preOp_age, preOp_mallampati, preOp_smoking, preOp_pain, treat,
								 intraOp_surgerySize, extubation_cough),
		label = list(
			preOp_gender ~ "Gender",
			preOp_asa ~ "ASA physical status",
			preOp_calcBMI ~ "BMI",
			preOp_age ~ "Age",
			preOp_mallampati ~ "Mallampati Score",
			preOp_smoking ~ "Smoking Status",
			preOp_pain ~ "Preoperative Pain",
			treat ~ "Intervention",
			intraOp_surgerySize ~ "Surgery Size",
			extubation_cough ~ "Amount	of	coughing	immediately	after
													extubation"
		),
missing_text = "Missing")
```

```{r}
#| label: tbl-lin
#| tbl-cap: "Linear Regression"
#| output-location: slide

#regression and results
linear_model <- lm(preOp_gender ~ preOp_asa + preOp_calcBMI + preOp_age,
									 data = lico)
tbl_regression(
	linear_model,
	intercept = TRUE,
	label = list(
		preOp_asa ~ "ASA physical status",
		preOp_calcBMI ~ "BMI",
		preOp_age ~ "Age"
		))
# There is no significant difference between gender and ASA, BMI, or Age in the study.
```

```{r}
#| label: fig-plots
#| fig-cap: "Histogram of Linear Regression"
#| output-location: slide

#figure
hist(lico$preOp_calcBMI)

```
@fig-plots contains a histogram.
@tbl-descr contains descriptive statistics.
```{r}
#| erro: true
#inline stats from gtsummary
table1 <- tbl_summary(
  lico,
  by = preOp_gender,
  	include = c(preOp_calcBMI, preOp_asa, preOp_age, preOp_pain)) |>
		add_overall(last = TRUE)
	table1

	inline_text(table1, variable = "preOp_calcBMI", column = "0")

#printing inline
pain_f <- inline_text(table1, variable = "preOp_pain", 
                         column = "0")
pain_m <- inline_text(table1, variable = "preOp_pain", 
                         column = "1")
```
A lower proportion of female (`r pain_f`) than male (`r pain_m`) participants are in preOp pain.

The data is from a randomized, double-blind, comparison of licorice vs sugar-water gargle for prevention of postop sore throat and postextubation coughing. The study includes variables like age, sex, gender, mallampati score, postop pain, extubation coughing, BMI,  smoking status, and outcomes.


